Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2018-02-22 pkg/disttree/inst/draft/draft.Rnw
added references in the application and computational detail section
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2034 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 37094590550942f9d36a0395f7dfd337ea39f181

Figure~\ref{map} shows a map of Tyrol with the location of all observation stations included in the data set. Each station is illustrated by a symbol with the type of symbol representing the method that performed best in terms of CRPS at this station. The color of the symbol indicates the difference between the CRPS of the distributional forest and the CRPS of the best performing among the other three models (prespecified GAM, boosted GAM and EMOS).
Even though for some stations, especially in East Tyrol, one of the two GAMs and for a few others the EMOS model leads to the best results, for the majority of stations the distributional forest performs best.

@@

\section*{Computational details}
The corresponding implementation to the novel methods presented in this article is available on \textsf{R}-Forge in an \textsf{R} package called \textbf{disttree} within the project \textbf{partykit} (\url{https://R-Forge.R-project.org/projects/partykit/}). The function \code{disttree} uses either the \code{mob} or \code{ctree} function as a framework to build a tree. Similarly, the function \code{distforest} is based on the \code{cforest} function which provides a framework to build a distributional forest. All three functions, \code{mob}, \code{ctree} and \code{cforest}, are provided in the package \textbf{partykit} (\citealt{Hothorn+Zeileis:2015}).

@@

%\newpage
\nocite{Messner+Mayr+Zeileis:2016, Stasinopoulos+Rigby:2007, Seibold+Zeileis+Hothorn:2016, Seibold+Zeileis+Hothorn:2017, Yee:2010, Hofner+Mayr+Schmid:2016, srtm}
% Zeileis+Wiel+Hornik:2008, 
% Zeileis+Hothorn+Hornik:2010, 
% hothorn2015package,

>>>>

Figure~\ref{map} shows a map of Tyrol (based on the SRTM 90m Digital Elevation Data, \cite{srtm}) with the location of all observation stations included in the data set. Each station is illustrated by a symbol with the type of symbol representing the method that performed best in terms of CRPS at this station. The color of the symbol indicates the difference between the CRPS of the distributional forest and the CRPS of the best performing among the other three models (prespecified GAM, boosted GAM and EMOS).
Even though for some stations, especially in East Tyrol, one of the two GAMs and for a few others the EMOS model leads to the best results, for the majority of stations the distributional forest performs best.

@@

\section*{Computational details}
The corresponding implementation to the novel methods presented in this article is available on \textsf{R}-Forge in an \textsf{R} package called \textbf{disttree} within the project \textbf{partykit} (\url{https://R-Forge.R-project.org/projects/partykit/}). The function \code{disttree} uses either the \code{mob} or \code{ctree} function as a framework to build a tree. Similarly, the function \code{distforest} is based on the \code{cforest} function which provides a framework to build a distributional forest. All three functions, \code{mob}, \code{ctree} and \code{cforest}, are provided in the package \textbf{partykit} (\citealt{Hothorn+Zeileis:2015}). To specify a distribution family the user can hand over one of the following objects as input argument in \code{distfit}, \code{disttree} and \code{distforest}: 
\begin{itemize}
\item a GAMLLS family object from the \textsf{R} package \textbf{gamlss.dist} (\citealt{Stasinopoulos+Rigby:2007}).
\item a family list generating function from the package \textbf{disttree}.
\item a complete family list from the package \textbf{disttree}.
\item a custom list containing all required information about the distribution family.
\end{itemize}

In Section~\ref{ProbabilisticForecasting} the prespecified GAMs were built using the function \code{gamlss} from the \textsf{R} package \textbf{gamlss.dist} (\citealt{Stasinopoulos+Rigby:2007}). For the boosted GAMs the function \code{gamboostLSS} from the \textsf{R} package \textbf{gamboostLSS} (\citealt{Hofner+Mayr+Schmid:2016}) was applied. The EMOS models were built using the function \code{crch} from the \textsf{R} package \textbf{crch} (\citealt{Messner+Mayr+Zeileis:2016})

@@

%\newpage
\nocite{Seibold+Zeileis+Hothorn:2016, Seibold+Zeileis+Hothorn:2017, Yee:2010}
% Zeileis+Wiel+Hornik:2008, 
% Zeileis+Hothorn+Hornik:2010,
